\normalsize{Real-Time Activity Classification by Matched Filtering using Body-Worn Accelerometers}

### 2016-10-10 notes/poster/poster.tex
Added more poster specifics

\title{\normalsize{Efficient Techniques for Simulations of Kinetic Equations of Gas Dynamics}}
\author{\small{Craig Euler, \hspace{5mm} College of Science and Mathematics ,\hspace{5mm} California State University Northridge}}
\footer{}
\date{}
% \includegraphics[scale=.2]{CSUN_seal.png}}

@@

	\begin{textblock}{19.5}(1,4)

\begin{block}{\small{Introduction}}
Numerical simulations of gas flows over sharp leading edges of air vehicles are challenging because they require the solution of model kinetic equations. These equations lead to stiff problems in regimes transitional from continuum to free molecular flow. The main difficulties in solving model kinetic equations include the loss of the conservation of mass, momentum, and energy, and low order convergence of solutions. Flows that are near continuum are well described by the Boltzmann equation with the BGK collision model:

@@

%A one dimensional reduction is performed on \eqref{ES-BGK} by assuming that no mass transfer occurs in two of the three directions in space, in this case $v_{2}$ and $v_{3}$. By considering the fallowing substitutions:

% f1
%\begin{equation*}
%\label{f1}
%f^{1} (t,x,v_{1}) = \int_{-\infty}^{\infty} \int_{-\infty}^{\infty} f(t, \vec{x}, \vec{v}) dv_{2} dv_{3}
%\end{equation*}
% use \ref{f1} or \eqref{f1} to get the reference for this equation

% f2
%\begin{equation*}
%\label{f2}
%f^{2} (t,x,v_{1}) = \int_{-\infty}^{\infty} \int_{-\infty}^{\infty} v_{2}^2 f(t, \vec{x}, \vec{v}) dv_{2} dv_{3}
%\end{equation*}
% use \ref{f2} or \eqref{f2} to get the reference for this equation

%then by integrating \eqref{ES-BGK} over all velocity space we are left with the following reduction with $j=1,2$:

@@

\begin{block}{\small{References}}
% http://depts.washington.edu/clawpack/users-4.6/about.html#authors
[1] R. J. LeVeque, M. J. Berger, et. al., Clawpack Software 4.5.1, www.clawpack.org, June 2011
\end{block}

>>>>

% Poster size can be: 36" wide by 44" tall

\title{\normalsize{Real-Time Activity Classification by Matched Filtering using Body-Worn Accelerometers}}
\author{\small{Craig~Euler craig.euler@gmail.com, C.T.~Lin ct.lin@csun.edu,\\Bryan~Juarez bryan.juarez.974@my.csun.edu, Melissa~Flores melissa.flores.455@my.csun.edu\\College of Engineering and Computer Science\\California State University, Northridge}}

\footer{}
\date{}

@@

\begin{textblock}{19.5}(1, 7)

\begin{block}{\small{Introduction}}

Various methods for activity classification using body-worn sensors exist.
Custom Decision Tree, Automatically Generated Decision Tree, and Artificial Neural Networks \cite{parkka_ermes_korpipaa_mantyjarvi_peltola_korhonen_2006} have been explored as well as other frequency based classification methods \cite{sharma_purwar_lee_lee_chung_2008}.
%The use of the matched-filter method for classification has been studied in the past \cite{giannakis_tsatsanis_1990} and we seek to adopt this method for our use to identify an individual\textquotesingle s activity for the purpose of real-time processing on a low-powered micro-controller.
The methods used for our algorithms are designed for computational efficiency to accommodate the resource limitations of a microcontroller. In this paper, we use the MSP432 microcontroller for our timing results.

%The algorithms described in this paper are used in two main modules: The activity classification module for real-time processing and the training module to train the device to identify the user\textquotesingle s activity.

The training module does not need to be performed in real time.
%This algorithm is the most demanding on computational resources and is only executed when training or re-training the unit to identify the user\textquotesingle s activity, which means that this can be performed on an external device such as a smart phone or tablet.
The purpose of the training module is to create the reference signals to be used on the microcontroller for the real-time activity classification processing.

The real-time activity classification module is intended to be performed on a low-powered microcontroller.
%This module reads in the references stored on the unit to be used as templates that the matched-filter will use for determining the individual\textquotesingle s activity.
Both of these modules use the same principles and hence the same algorithm kernels.

@@

@@

\begin{block}{\small{References}}
\bibliographystyle{plain}
\bibliography{reference}
